Titeltext

### 2018-07-26 thesis/paper/paper.tex
Added none of

>>>>

\subsection{None of (Q52558054)}
The none of constraint restricts the values that the property may refer to by listing a set of values as forbidden.

\begin{table}[H]
\caption{None of constraint (Q52558054)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & constrained statement \\
\hline
Qualifiers & \makecell{forbidden value (P2305) -- 1..* \\ values that may not appear in a constrained property} \\
\hline
Violation & \makecell{constrained statement with a forbidden value} \\
\hline
Dependency & constrained statement \\
\hline
\end{tabularx}
\end{table}

Modelling this constraint is very straightforward, since each forbidden value forms a property-value pair with the constrained statement that may not exists. Thus a violations is a tripleEDB with the constrained statement and a forbidden value.
